Equations & R Code

### 2016-12-28 manuscript/coexistence-stability_ms.Rmd
updates fig 1 background to white

mytheme <- theme_bw()+
  theme(panel.grid.major.x = element_blank(), 
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.y = element_line(color="white"),
        panel.background   = element_rect(fill = "#EFEFEF"),
        axis.text          = element_text(size=6, color="grey35", family = "Arial Narrow"),
        axis.title         = element_text(size=8, family = "Arial Narrow", face = "bold"),
        panel.border       = element_blank(),
        axis.line.x        = element_line(color="black"),
        axis.line.y        = element_line(color="black"),
        strip.background   = element_blank(),
        strip.text         = element_text(size=8, color="grey35", family = "Arial Narrow"),
        legend.title       = element_text(size=8, family = "Arial Narrow"),
        legend.text        = element_text(size=6, color="grey35", family = "Arial Narrow"),
        legend.key.size    = unit(0.3, "cm"))

# mycols <- c("#9D6188","#97A861")
# mycols <- c("black", "red")
# mycols <- c("grey35", "steelblue")
mycols <- viridis(2, end = 0.8)

>>>>

# mytheme <- theme_bw()+
#   theme(panel.grid.major.x = element_blank(), 
#         panel.grid.minor.x = element_blank(),
#         panel.grid.minor.y = element_blank(),
#         panel.grid.major.y = element_blank(),
#         panel.background   = element_rect(fill = "white"),
#         axis.text          = element_text(size=6, color="grey35", family = "Arial Narrow"),
#         axis.title         = element_text(size=8, family = "Arial Narrow", face = "bold"),
#         panel.border       = element_blank(),
#         axis.line.x        = element_line(color="black"),
#         axis.line.y        = element_line(color="black"),
#         strip.background   = element_blank(),
#         strip.text         = element_text(size=8, color="grey35", family = "Arial Narrow"),
#         legend.title       = element_text(size=8, family = "Arial Narrow"),
#         legend.text        = element_text(size=6, color="grey35", family = "Arial Narrow"),
#         legend.key.size    = unit(0.3, "cm"))

mytheme <- theme_few()+
  theme(axis.text          = element_text(size=6, color="grey35"),
        axis.title         = element_text(size=8),
        strip.text         = element_text(size=8, color="grey35"),
        legend.title       = element_text(size=8),
        legend.text        = element_text(size=6, color="grey35"),
        legend.key.size    = unit(0.3, "cm"))

# mycols <- c("#9D6188","#97A861")
# mycols <- c("black", "red")
# mycols <- c("grey35", "steelblue")
mycols <- viridis(2, end = 0.6)
